Vizualizing Toronto Homess Shelter data Across a Global Pandemic

### 2022-02-07 outputs/paper/paper.Rmd
FINAL COMMIT

---
title: "Vizualizing Toronto Homess Shelter data Across a Global Pandemic"
subtitle: "A Look Into How The Pandemic disrupted the Flow Of Homeless Shelters And How The Situation Has Improved Since"
author: 
  - Adam Labas
thanks: "Code and data are available at: https://github.com/adam-labas/adam_labas_paper_1_opendatatoronto"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In addition to a global pandemic, homlessness and housing is a self apparent issue in the city of Toronto. Taking a stroll through certain areas in the downtown core, it's almost impossible to miss homeless tent cities and homeless people lined outside of shelters awaiting food or entry in the afternoon. Upon further examination of data collected from the Open Data Portal of the City of Toronto, it was easy to find interesting trends in homeless shelter data in the years 2020 and 2021. We found trends in the diminishing use of shelters by various demographic of homeless people and age groups. This paper attempts to visualize these trends as well as touch on some problems that one might experience in trying to extract real meaning from the data."
output:
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
toc: TRUE
bibliography: references.bib
---

>>>>

---
title: "Vizualizing Toronto Homess Shelter data Across a Global Pandemic"
subtitle: "A Look Into How The Pandemic disrupted the Flow Of Homeless Shelters And How The Situation Has Improved Since"
author: 
  - Adam Labas
thanks: "Code and data are available at: https://github.com/adam-labas/adam_labas_paper_1_opendatatoronto"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In addition to a global pandemic, homelessness and housing is a self apparent issue in the city of Toronto. Taking a stroll through certain areas in the downtown core, it's almost impossible to miss homeless tent cities and homeless people lined outside of shelters awaiting food or entry in the afternoon. Upon further examination of data collected from the Open Data Portal of the City of Toronto, it was easy to find interesting trends in homeless shelter data in the years 2020 and 2021. We found trends in the diminishing use of shelters by various demographic of homeless people and age groups. This paper attempts to visualize these trends as well as touch on some problems that one might experience in trying to extract real meaning from the data."
output:
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
toc: TRUE
bibliography: references.bib
---
